Smart Drill-Down

### 2015-02-17 TableSummarization/Paper/algorithms.tex
small changes throughout

\begin{lemma}\label{lemma:rule-ordering}
Let $R$ be a rule-list. Let $R^{\prime}$ be the rule-list having the same rules as $R$, but ordered in descending order by weight. Then
$$\text{Score}(R^{\prime}) \geq \text{Score}(R)$$
\end{lemma}
\papertext{The proof of this lemma, as well as other proofs, can be found in the appendix of the technical report~\cite{tr}}\techreporttext{The proof of this lemma, as well as other proofs, can be found in the appendix}.

\noindent Thus, it is sufficient to restrict our attention to rule-lists that have rules sorted in decreasing order by weight. Or equivalently, we can define Score for a \emph{set} of rules as follows:

\begin{definition}\label{def:set-score}
Let $R$ be a set of rules. Then the Score of $R$ is
$$\text{Score}(R) = \text{Score}(R^{\prime})$$
where $R^{\prime}$ is the list of rules obtained by ordering the rules in the set $R$ in decreasing order by weight.
\end{definition}

@@

\begin{lemma}\label{lemma:submodular}
For a given table $T$, the Score function over sets $S$ of rules, defined by the following is submodular:
$$\text{Score}(S) = \sum_{r \in S} MCount(r,S)W(r)$$
\end{lemma}

>>>>

\begin{lemma}\label{lemma:rule-ordering}
Let $R$ be a rule-list. Let $R^{\prime}$ be the rule-list having the same rules as $R$, but ordered in descending order by weight. Then
$\text{Score}(R^{\prime}) \geq \text{Score}(R)$.
\end{lemma}
\papertext{The proof of this lemma, as well as other proofs, can be found in the appendix of the technical report~\cite{tr}}\techreporttext{The proof of this lemma, as well as other proofs, can be found in the appendix}. 
Thus, it is sufficient to restrict our attention to rule-lists that have rules sorted in decreasing order by weight. Or equivalently, we can define Score for a \emph{set} of rules as follows:

\begin{definition}\label{def:set-score}
Let $R$ be a set of rules. Then the Score of $R$ is
$\text{Score}(R) = \text{Score}(R^{\prime})$
where $R^{\prime}$ is the list of rules obtained by ordering the rules in the set $R$ in decreasing order by weight.
\end{definition}

@@

\begin{lemma}\label{lemma:submodular}
For a given table $T$, the Score function over sets $S$ of rules, defined by the following is submodular:
$$\text{Score}(S) = \sum_{r \in S} MCount(r,S)W(r)$$
\end{lemma}
\vspace{-10pt}

### 2015-02-17 TableSummarization/Paper/exp.tex
small changes throughout

\section{Experiments}\label{sec:experiments}
We have implemented a fully-functional interactive system instrumented with the smart drill down operator, with a web interface.
We now describe our experiments on this system with real datasets.

@@

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=90mm]{graphs/screenshots6col/empty_expansion.jpg}
\caption{Summary after clicking on the empty rule \label{fig:uiexample1}}
\vspace{-15pt}
\end{figure}

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=90mm]{graphs/screenshots6col/age_drilldown.jpg}
\caption{A regular drill down on Age\label{fig:drilldownexample}}
\end{figure}

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=90mm]{graphs/screenshots6col/empty_expansion.jpg}
\vspace{-10pt}
\caption{Star expansion on `Education' Column \label{fig:uiexamplestar}}
\vspace{-15pt}
\end{figure}

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=90mm]{graphs/screenshots6col/empty_expansion.jpg}
\vspace{-10pt}
\caption{A rule expansion \label{fig:uiexamplerule}}
\vspace{-15pt}
\end{figure}

@@

@@

@@

@@

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=90mm]{graphs/screenshots6col/bits_scoring.jpg}
\caption{Bits scoring\label{fig:weigtingbitwise}}
\end{figure}

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=90mm]{graphs/screenshots6col/min2_scoring.jpg}
\vspace{-10pt}
\caption{Size minus one weighting \label{fig:weightingsizeminusone}}
\vspace{-15pt}
\end{figure}

>>>>

\section{Experiments}\label{sec:experiments}
We have implemented a fully-functional interactive tool instrumented with the smart drill down operator, having a web interface.
We now describe our experiments on this tool with real datasets.

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=80mm,frame]{graphs/screenshots6col/empty_expansion.jpg}
\vspace{-10pt}
\caption{Summary after clicking on the empty rule \label{fig:uiexample1}}
\vspace{-15pt}
\end{figure}

@@

@@

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=80mm,frame]{graphs/screenshots6col/age_drilldown.jpg}
\vspace{-10pt}
\caption{A regular drill down on Age\label{fig:drilldownexample}}
\vspace{-5pt}
\end{figure}

@@

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=80mm,frame]{graphs/screenshots6col/empty_expansion.jpg}
\vspace{-10pt}
\caption{Star expansion on `Education' Column \label{fig:uiexamplestar}}
\vspace{-20pt}
\end{figure}

@@

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=80mm,frame]{graphs/screenshots6col/empty_expansion.jpg}
\vspace{-10pt}
\caption{A rule expansion \label{fig:uiexamplerule}}
\vspace{-15pt}
\end{figure}

@@

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=80mm,frame]{graphs/screenshots6col/bits_scoring.jpg}
\vspace{-10pt}
\caption{Bits scoring\label{fig:weigtingbitwise}}
\end{figure}

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=80mm,frame]{graphs/screenshots6col/min2_scoring.jpg}
\vspace{-10pt}
\caption{Size minus one weighting \label{fig:weightingsizeminusone}}
\vspace{-15pt}
\end{figure}

### 2015-02-17 TableSummarization/Paper/intro.tex
small changes throughout

To reiterate, our chief contribution in this paper is the {\em smart drill down} interaction operator,
an extension of traditional drill down, aimed at allowing analysts to zoom into the
more ``interesting'' parts of a dataset. In addition to this operator,
we develop techniques to support this operator on increasingly larger datasets:
\squishlist
\item {\em Basic Interaction:} We demonstrate that finding the optimal list of rules is {\sc NP-Hard},
and we develop an algorithm to find the approximately optimal list of rules to display when the user performs a smart drill down operation. 
\item {\em Dynamic Sample Maintenance:} To improve response time on large tables, we formalize the problem of dynamically
maintaining samples in memory to support smart drill down. 
We show that optimal identification of samples is once again {\sc NP-Hard}, and 
we develop an approximate scheme for dynamically maintaining and using multiple samples of the table in memory.
\squishend

>>>>

To reiterate, our chief contribution in this paper is the {\em smart drill down} interaction operator,
an extension of traditional drill down, aimed at allowing analysts to zoom into the
more ``interesting'' parts of a dataset. In addition to this operator,
we develop techniques to support this operator on increasingly larger datasets:
\squishlist
\item {\em Basic Interaction:} We demonstrate that finding the optimal list of rules is {\sc NP-Hard},
and we develop an algorithm to find the approximately optimal list of rules to display when the user performs a smart drill down operation. 
\item {\em Dynamic Sample Maintenance:} To improve response time on large tables, we formalize the problem of dynamically
maintaining samples in memory to support smart drill down. 
We show that optimal identification of samples is once again {\sc NP-Hard}, and 
we develop an approximate scheme for dynamically maintaining and using multiple samples of the table in memory.
\squishend
We have developed a {\em fully functional and usable prototype tool} that supports the smart drill-down operator. From this point on, when we provide result snippets, these will be screenshots from our prototype tool. Our prototype tool also supports traditional drill-down: smart drill-down 
can be viewed as a generalization of traditional drill-down (with the weighting function set appropriately). In Section~\ref{sec:exp_qualitative}, we compare smart drill-down with traditional drill-down and show that smart drill-down returns considerably better results.

### 2015-02-17 TableSummarization/Paper/related.tex
small changes throughout

Some related work~\cite{Golab_efficientand, Golab:2008:GNT:1453856.1453900} focuses on finding minimum sized Tableaux that provide improved support and confidence for conditional functional dependencies. There has also been work~\cite{Bu:2005:MSH:1083592.1083644, Lakshmanan:2002:GMA:1287369.1287435, Xiang_succinctsummarization, Geerts04tilingdatabases} on finding hyper-rectangle based covers for tables. In both these cases, the emphasis is on completely covering or 
summarizing the table, suffering from the same problems as traditional drill down in that the user may be presented with
too many results. The techniques in the former case may end up picking rare ``patterns'' if they have high confidence, and in the latter case do not scale well to a large number of attributes (in their case, $\geq 4$).

>>>>

Some related work~\cite{DBLP:journals/debu/GolabKS11, Golab:2008:GNT:1453856.1453900} focuses on finding minimum sized Tableaux that provide improved support and confidence for conditional functional dependencies. There has also been work~\cite{Bu:2005:MSH:1083592.1083644, Lakshmanan:2002:GMA:1287369.1287435, DBLP:conf/kdd/XiangJFD08, Geerts04tilingdatabases} on finding hyper-rectangle based covers for tables. In both these cases, the emphasis is on completely covering or 
summarizing the table, suffering from the same problems as traditional drill down in that the user may be presented with
too many results. The techniques in the former case may end up picking rare ``patterns'' if they have high confidence, and in the latter case do not scale well to a large number of attributes (in their case, $\geq 4$).
